---
title: "Generalised Technique B - AUC Analysis"
author: "Luka Kuchalskyte (s3983471)"
date: "`r Sys.Date()`"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Scenario 1

**Scenario 1**: A model is trained on the full dataset, and predictions are made for both “Blue” and “Red” individuals separately. AUC is calculated for each group to assess predictive accuracy.

This scenario involves evaluating the predictive performance of a model for two demographic groups ("Blue" and "Red") by calculating the Area Under the Curve (AUC) for each group. The analysis aims to assess whether there is a significant difference in the model's predictive accuracy between the two groups. This is particularly important for detecting bias in the model. By bootstrapping the analysis, we can quantify the variability in AUC values and formally test for differences between groups.

1. Train the Model on the Full Dataset.
  - A machine learning model (logistic regression) is trained on the entire dataset, which includes both "Blue" and "Red" individuals.
  - The model uses income and education to predict the target variable (undesired outcome: 0 = desired, 1 = undesired).

2. Stratified Predictions.
  - Predictions are made for all individuals in the dataset.
  - The dataset is split into two subgroups based on the sensitive characteristic "Colour":
    * Group 1: Individuals with Colour = BLUE
    * Group 2: Individuals with Colour = RED
    
3. AUC Calculation for Each Group.
  - The AUC, a measure of predictive performance, is calculated separately for each group:
    * AUC for "Blue" individuals (AUC BLUE)
    * AUC for "Red" individuals (AUC RED)
  - The AUC is a robust performance metric for binary classification models, as it evaluates the model's ability to distinguish between positive and negative outcomes, regardless of threshold.
  
4. Bootstrapping to Generate AUC Distributions.
  - To assess the variability in AUC across the two groups, the process is repeated for n bootstrap samples:

5. Comparing the AUC Distributions with an ANOVA.

```{r}
stratified_bootstrap <- function(data, variable1, 
                                 variable2, n_resamples = 100, 
                                 seed) {
  
  # In: data: A data frame containing the variables of interest;
  #     variable1: A string indicating the first sensitive variable;
  #     variable2: A string indicating the second sensitive variable;
  #     n_resamples: The number of bootstrap resamples to generate;
  #     seed: The random seed used for the sampling.
  # Out:  A list of bootstrap samples maintaining the proportional representation of Colour and Disability.
  
  # Load relevant package
  library(dplyr)
  
  # Set a seed for reproducability
  set.seed(seed) 

  # Calculate the original proportions of each demographic group
  original_proportions <- data %>%
    group_by(!!sym(variable1), !!sym(variable2)) %>%
    summarise(n = n(), .groups = "drop") %>%
    mutate(proportion = n / sum(n))

  # Initialize an empty list to store the bootstrap samples
  bootstrap_samples <- list()

  # Perform stratified bootstrapping
  for (i in 1:n_resamples) {
    
    # Initialize an empty data frame for each bootstrap sample
    bootstrap_sample <- data.frame()

    # Resample within each demographic group to maintain group proportions
    for (j in 1:nrow(original_proportions)) {
      
      # Filter data for the current group
      group_data <- data %>%
        filter(!!sym(variable1) == original_proportions[[variable1]][j],
               !!sym(variable2) == original_proportions[[variable2]][j])

      # Calculate the number of samples to draw from this group
      n_samples <- round(original_proportions$proportion[j] * nrow(data))

      # Draw a bootstrap sample from the group with replacement
      group_resample <- group_data[sample(1:nrow(group_data), size = n_samples, 
                                          replace = TRUE), ]

      # Bind the resampled group data to the bootstrap sample
      bootstrap_sample <- rbind(bootstrap_sample, group_resample)
    }
    
    # Store the bootstrap sample in the list
    bootstrap_samples[[i]] <- bootstrap_sample
  }
  
  # Return the list of bootstrap samples
  return(bootstrap_samples)
}
```

```{r}
# Function for Scenario 1: Train on Full dataset and Test on Blue/Red
auc_anova_1 <- function(data, variable1, 
                        variable2, n_resamples = 100, 
                        seed, dist, formula, 
                        group1, group2,
                        family = binomial, response, type = "response") {
  
  #  In: data: The dataset used for bootstrapping and modeling;
  #      variable1: A string indicating the first sensitive variable;
  #      variable2: A string indicating the second sensitive variable;
  #      n_resamples: Number of resamples for stratified bootstrapping (default = 100);
  #      seed: Seed for reproducibility;
  #      dist: Proportion for splitting data into train and test sets;
  #      formula: A formula specifying the model;
  #      group1: First class of variable1 = 0 (e.g. "Female");
  #      group2: Second class of variable1 = 1 (e.g. "Male");
  #      family: The family for the GLM model (default = binomial);
  #      response: The name of the response variable as a string;
  #      type: The type of prediction (default = "response").
  # Out: A list containing the following elements:
  #      - mean_auc: A summary data frame with mean AUC values for groups.
  #      - AUC_result: A data frame in long format containing the AUC values 
  #                    for each bootstrap iteration and each group.
  #                    Columns include:
  #                      * Bootstrap: The bootstrap iteration number.
  #                      * Group: The group for which AUC is calculated.
  #                      * AUC: The AUC value for that group in the given iteration.
  #      - anova_result: The summary of an ANOVA test performed on the AUC values
  #                      to assess whether there are significant differences 
  #                      between the groups.
  #      - visualisation: A ggplot2 density plot showing the distribution of AUC 
  #                       values for the groups across all bootstrap samples.
  
  # Load necessary packages
  library(dplyr)
  library(pROC)
  library(ggplot2)
  library(kableExtra)  # For APA-style table formatting
  library(viridis)
  
  # Generate n_bootstrap samples using the bootstrap function
  bootstrap_samples <- stratified_bootstrap(data = data, 
                                            variable1 = variable1, 
                                            variable2 = variable2, 
                                            n_resamples = n_resamples,
                                            seed = seed)

  # Initialize a data frame to store AUC results in long format
  auc_results <- data.frame(Bootstrap = integer(n_resamples * 2), 
                            Group = character(n_resamples * 2), 
                            AUC = numeric(n_resamples * 2),
                            stringsAsFactors = FALSE)  # Prevent factors
  
  # Loop through each bootstrap sample
  for (i in 1:n_resamples) {
    
    # Get the current bootstrap sample
    sample <- bootstrap_samples[[i]]
    
    # Split the bootstrap sample into train and test sets
    set.seed(seed)
    test.index <- sample(nrow(sample), nrow(sample) * dist) 
    train <- sample[-test.index, ]
    test <- sample[test.index, ]
    
    # Train the model on the training data
    model <- glm(formula = formula, data = train, family = family)
    
    # Predict outcomes separately for groups
    test_g1 <- test %>% filter(!!sym(variable1) == 0)
    test_g2 <- test %>% filter(!!sym(variable1) == 1)

    # Predict probabilities for groups
    predictions_g1 <- predict(model, newdata = test_g1, type = "response")
    predictions_g2 <- predict(model, newdata = test_g2, type = "response")
    
    # Calculate AUC for groups separately
    auc_g1 <- if (nrow(test_g1) > 0) {
      roc(test_g1[[response]], predictions_g1)$auc
    } else NA

    auc_g2 <- if (nrow(test_g2) > 0) {
      roc(test_g2[[response]], predictions_g2)$auc
    } else NA
    
    # Store results in long-format data frame
    auc_results[(i-1)*2 + 1, ] <- c(i, group1, as.numeric(auc_g1))
    auc_results[(i-1)*2 + 2, ] <- c(i, group2, as.numeric(auc_g2))
  }

  # Ensure AUC is numeric (in case of coercion issues)
  auc_results$AUC <- as.numeric(auc_results$AUC)
  
  # Calculate Mean AUC values for each group
  mean_auc <- auc_results %>%
    group_by(Group) %>%
    summarize(mean_AUC = mean(AUC, na.rm = TRUE), 
              SD = sd(AUC, na.rm = TRUE)) %>%
    ungroup() %>%
    mutate(mean_AUC = sprintf("%.3f", mean_AUC),
           SD = sprintf("%.3f", SD))
  
  # Format mean_auc as APA-style table
  mean_auc_apa <- mean_auc %>%
    kable(format = "html", col.names = c("Group", "Mean AUC", "SD"),
          caption = "Mean AUC and Standard Deviation for Groups") %>%
    kable_styling(full_width = FALSE, position = "center")
  
  # Perform ANOVA on AUC results to test if there are significant differences between groups
  anova_model <- aov(AUC ~ Group, data = auc_results)
  anova_summary <- summary(anova_model)
  
  # Format AUC results as APA-style table
  auc_results_apa <- auc_results %>%
    mutate(AUC = sprintf("%.3f", AUC)) %>%
    kable(format = "html", col.names = c("Bootstrap Sample", "Group", "AUC"),
          caption = "Bootstrap Results: AUC for Each Group") %>%
    kable_styling(full_width = FALSE, position = "center")
  
  # Plot the AUC distributions for each  group
  plot <- ggplot(auc_results, aes(x = AUC, fill = Group)) +
    geom_density(alpha = 0.7) +  # Density plot with transparency
    labs(title = "Density Plot of AUC Distributions by Group",
         x = "AUC",
         y = "Density",
         caption = "Data represents bootstrap samples") +
    theme_minimal() +  # Use a minimal theme for a clean look
    scale_fill_viridis_d(option = "magma", begin = 0.2, end = 0.8) +  # Use the "magma" palette from viridis
    theme(plot.title = element_text(hjust = 0.5, size = 14),  # Center and style title
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12),
          legend.title = element_blank())  # Remove legend title for simplicity

  # Return the auc results, anova results and visualisation
  return(list(
    mean_auc = mean_auc_apa,       # APA-formatted mean AUC table
    AUC_result = auc_results_apa,  # APA-formatted bootstrap AUC table
    anova_result = anova_summary,  # Summary of the ANOVA test
    visualisation = plot))         # Density plot visualizing the AUC distribution for groups
}
```

# 2. Scenario 2A

**Scenario 2A**: A model is trained only on the first group and tested separately on both groups, with AUC calculated for each.

```{r}
# Function for Scenario 2A: Train on g1 and Test on g1/g2
auc_anova_2 <- function(data, variable1, variable2, 
                        n_resamples = 100, seed, dist = 0.2, 
                        group1, group2,
                        formula, family = binomial, response) {
  
  # In: data: The dataset used for bootstrapping and modeling;
  #      variable1: A string indicating the first categorical variable;
  #      variable2: A string indicating the second categorical variable;
  #      n_resamples: Number of resamples for stratified bootstrapping (default = 100);
  #      seed: Seed for reproducibility;
  #      dist: Proportion for splitting data into train and test sets (default = 0.2);
  #      group1: First class of variable1 = 0 (e.g. "Female");
  #      group2: Second class of variable1 = 1 (e.g. "Male");
  #      formula: A formula specifying the model;
  #      family: The family for the GLM model (default = binomial);
  #      response: The name of the response variable as a string.
  # Out: A list containing the following elements:
  #      - mean_auc: A data frame summarizing the mean AUC values for each train-test scenario.
  #                 * train_color: The group on which the model was trained (e.g., "Blue").
  #                 * test_color: The group on which the model was tested (e.g., "Blue" or "Red").
  #                 * mean_auc: The average AUC across all bootstrap iterations for the given scenario.
  #      - AUC_result: A data frame in long format containing the AUC values 
  #                    for each bootstrap iteration and each group (Blue and Red).
  #                    Columns include:
  #                  * Bootstrap: The bootstrap iteration number.
  #                  * Group: The group (Blue or Red) for which AUC is calculated.
  #                  * AUC: The AUC value for that group in the given iteration.
  #      - anova_result: The summary of an ANOVA test performed on the AUC values
  #                      to assess whether there are significant differences 
  #                      between the Blue and Red groups.
  #      - visualisation: A ggplot2 density plot visualizing the distribution of AUC values 
  #                       for each train-test scenario ("Blue on Blue" and "Blue on Red"). 
  
  # Load required packages
  library(dplyr)
  library(pROC)
  library(ggplot2)
  library(kableExtra)  # For APA-style table formatting
  library(viridis)
  
  # Generate n_bootstrap samples using the bootstrap function
  bootstrap_samples <- stratified_bootstrap(data = data, 
                                            variable1 = variable1, 
                                            variable2 = variable2, 
                                            n_resamples = n_resamples,
                                            seed = seed)
  
  # Initialize a data frame to store AUC results in long format
  auc_results <- data.frame(Bootstrap = integer(), 
                            Train_Group = character(), 
                            Test_Group = character(), 
                            AUC = numeric())

  # Loop through each bootstrap sample
  for (i in 1:n_resamples) {
    
    # Get the current bootstrap sample
    sample <- bootstrap_samples[[i]]
    
    # Split the bootstrap sample into train and test sets
    set.seed(seed)
    test.index <- sample(nrow(sample), nrow(sample) * dist) 
    train <- sample[-test.index, ]
    test <- sample[test.index, ]

    # Train on the group1 
    g1_train <- train %>% filter(!!sym(variable1) == 0)  # Filter rows where variable1 = 0
    if (nrow(g1_train) > 0) {
    
      # Train a GLM model on the group1 training set
      g1_model <- glm(formula = formula, data = g1_train, family = family)

      # Test on group1 group
      test_g1 <- test %>% filter(!!sym(variable1) == 0)
      if (nrow(test_g1) > 0) {
        # Predict probabilities and calculate AUC
        test_g1$predicted_prob <- predict(g1_model, newdata = test_g1, type = "response")
        auc_g1_test <- roc(test_g1[[response]], test_g1$predicted_prob)$auc
        
        # Store the result
        auc_results <- rbind(auc_results, data.frame(Bootstrap = i, 
                                                     Train_Group = group1, 
                                                     Test_Group = group1, 
                                                     AUC = as.numeric(auc_g1_test)))
      }

      # Test on group2 group
      test_g2 <- test %>% filter(!!sym(variable1) == 1)  # Filter rows where variable1 = 1
      if (nrow(test_g2) > 0) {
        # Predict probabilities and calculate AUC
        test_g2$predicted_prob <- predict(g1_model, newdata = test_g2, type = "response")
        auc_g2_test <- roc(test_g2[[response]], test_g2$predicted_prob)$auc
        
        # Store the result
        auc_results <- rbind(auc_results, data.frame(Bootstrap = i, 
                                                     Train_Group = group1, 
                                                     Test_Group = group2, 
                                                     AUC = as.numeric(auc_g2_test)))
      }
    }
  }

  # Calculate Mean AUC values
  mean_auc <- auc_results %>%
    group_by(Train_Group, Test_Group) %>%
    summarize(mean_AUC = mean(AUC, na.rm = TRUE), 
              SD = sd(AUC, na.rm = TRUE)) %>%
    ungroup() %>%
    mutate(mean_AUC = sprintf("%.3f", mean_AUC),
           SD = sprintf("%.3f", SD))
  
  # Format mean_auc as APA-style table
  mean_auc_apa <- mean_auc %>%
    kable(format = "html", col.names = c("Train Group", "Test Group", "Mean AUC", "SD"),
          caption = "Mean AUC and Standard Deviation for Train-Test Scenarios") %>%
    kable_styling(full_width = FALSE, position = "center")

  # Perform ANOVA on AUC results
  anova_model <- aov(AUC ~ Test_Group, data = auc_results)
  anova_summary <- summary(anova_model)
  
  # Format AUC results as APA-style table
  auc_results_apa <- auc_results %>%
    mutate(AUC = sprintf("%.3f", AUC)) %>%
    kable(format = "html", col.names = c("Bootstrap Sample", "Train Group", "Test Group", "AUC"),
          caption = "Bootstrap Results: AUC for Each Train-Test Scenario") %>%
    kable_styling(full_width = FALSE, position = "center")
  
  # Plot AUC distributions
  plot <- ggplot(auc_results, aes(x = AUC, fill = Test_Group)) +
    geom_density(alpha = 0.7) +  # Density plot with transparency
    labs(title = "Density Plot of AUC Distributions for Train-Test Scenarios",
         x = "AUC",
         y = "Density",
         caption = "Data represents bootstrap samples") +
    theme_minimal() +  # Use a minimal theme for a clean look
    scale_fill_viridis_d(option = "magma", begin = 0.2, end = 0.8) +  # Use the "magma" palette from viridis
    theme(plot.title = element_text(hjust = 0.5, size = 14),  # Center and style title
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12),
          legend.title = element_blank())  # Remove legend title for simplicity
  
  # Return results
  return(list(
    mean_auc = mean_auc_apa,       # APA-formatted mean AUC table
    AUC_result = auc_results_apa,  # APA-formatted bootstrap AUC table
    anova_result = anova_summary,  # Summary of the ANOVA test
    visualisation = plot))         # Density plot visualizing the AUC distribution
}
```

# 3. Scenario 2B

**Scenario 2B**: A model is trained only on the second group and tested separately on both groups, with AUC calculated for each.

```{r}
# Function for Scenario 2B: Train on g2 and Test on g1/g2
auc_anova_3 <- function(data, variable1, variable2, 
                        n_resamples = 100, seed, dist = 0.2, 
                        group1, group2,
                        formula, family = binomial, response) {
  
  # In: data: The dataset used for bootstrapping and modeling;
  #      variable1: A string indicating the first categorical variable;
  #      variable2: A string indicating the second categorical variable;
  #      n_resamples: Number of resamples for stratified bootstrapping (default = 100);
  #      seed: Seed for reproducibility;
  #      dist: Proportion for splitting data into train and test sets (default = 0.2);
  #      group1: First class of variable1 = 0 (e.g. "Female");
  #      group2: Second class of variable1 = 1 (e.g. "Male");
  #      formula: A formula specifying the model;
  #      family: The family for the GLM model (default = binomial);
  #      response: The name of the response variable as a string.
  # Out: A list containing the following elements:
  #      - mean_auc: A data frame summarizing the mean AUC values for each train-test scenario.
  #                 * train_color: The group on which the model was trained (e.g., "Blue").
  #                 * test_color: The group on which the model was tested (e.g., "Blue" or "Red").
  #                 * mean_auc: The average AUC across all bootstrap iterations for the given scenario.
  #      - AUC_result: A data frame in long format containing the AUC values 
  #                    for each bootstrap iteration and each group (Blue and Red).
  #                    Columns include:
  #                  * Bootstrap: The bootstrap iteration number.
  #                  * Group: The group (Blue or Red) for which AUC is calculated.
  #                  * AUC: The AUC value for that group in the given iteration.
  #      - anova_result: The summary of an ANOVA test performed on the AUC values
  #                      to assess whether there are significant differences 
  #                      between the Blue and Red groups.
  #      - visualisation: A ggplot2 density plot visualizing the distribution of AUC values 
  #                       for each train-test scenario ("Blue on Blue" and "Blue on Red"). 
  
  # Load required packages
  library(dplyr)
  library(pROC)
  library(ggplot2)
  library(kableExtra)  # For APA-style table formatting
  library(viridis)
  
  # Generate n_bootstrap samples using the bootstrap function
  bootstrap_samples <- stratified_bootstrap(data = data, 
                                            variable1 = variable1, 
                                            variable2 = variable2, 
                                            n_resamples = n_resamples,
                                            seed = seed)
  
  # Initialize a data frame to store AUC results in long format
  auc_results <- data.frame(Bootstrap = integer(), 
                            Train_Group = character(), 
                            Test_Group = character(), 
                            AUC = numeric())

  # Loop through each bootstrap sample
  for (i in 1:n_resamples) {
    
    # Get the current bootstrap sample
    sample <- bootstrap_samples[[i]]
    
    # Split the bootstrap sample into train and test sets
    set.seed(seed)
    test.index <- sample(nrow(sample), nrow(sample) * dist) 
    train <- sample[-test.index, ]
    test <- sample[test.index, ]

    # Train on the group2 
    g2_train <- train %>% filter(!!sym(variable1) == 1)  # Filter rows where variable1 = 1
    if (nrow(g2_train) > 0) {
    
      # Train a GLM model on the group2 training set
      g2_model <- glm(formula = formula, data = g2_train, family = family)

      # Test on group2 group
      test_g2 <- test %>% filter(!!sym(variable1) == 1)
      if (nrow(test_g2) > 0) {
        # Predict probabilities and calculate AUC
        test_g2$predicted_prob <- predict(g2_model, newdata = test_g2, type = "response")
        auc_g2_test <- roc(test_g2[[response]], test_g2$predicted_prob)$auc
        
        # Store the result
        auc_results <- rbind(auc_results, data.frame(Bootstrap = i, 
                                                     Train_Group = group2, 
                                                     Test_Group = group2, 
                                                     AUC = as.numeric(auc_g2_test)))
      }

      # Test on group1 group
      test_g1 <- test %>% filter(!!sym(variable1) == 0)  # Filter rows where variable1 = 0
      if (nrow(test_g1) > 0) {
        # Predict probabilities and calculate AUC
        test_g1$predicted_prob <- predict(g2_model, newdata = test_g1, type = "response")
        auc_g1_test <- roc(test_g1[[response]], test_g1$predicted_prob)$auc
        
        # Store the result
        auc_results <- rbind(auc_results, data.frame(Bootstrap = i, 
                                                     Train_Group = group2, 
                                                     Test_Group = group1, 
                                                     AUC = as.numeric(auc_g1_test)))
      }
    }
  }

  # Calculate Mean AUC values
  mean_auc <- auc_results %>%
    group_by(Train_Group, Test_Group) %>%
    summarize(mean_AUC = mean(AUC, na.rm = TRUE), 
              SD = sd(AUC, na.rm = TRUE)) %>%
    ungroup() %>%
    mutate(mean_AUC = sprintf("%.3f", mean_AUC),
           SD = sprintf("%.3f", SD))
  
  # Format mean_auc as APA-style table
  mean_auc_apa <- mean_auc %>%
    kable(format = "html", col.names = c("Train Group", "Test Group", "Mean AUC", "SD"),
          caption = "Mean AUC and Standard Deviation for Train-Test Scenarios") %>%
    kable_styling(full_width = FALSE, position = "center")

  # Perform ANOVA on AUC results
  anova_model <- aov(AUC ~ Test_Group, data = auc_results)
  anova_summary <- summary(anova_model)
  
  # Format AUC results as APA-style table
  auc_results_apa <- auc_results %>%
    mutate(AUC = sprintf("%.3f", AUC)) %>%
    kable(format = "html", col.names = c("Bootstrap Sample", "Train Group", "Test Group", "AUC"),
          caption = "Bootstrap Results: AUC for Each Train-Test Scenario") %>%
    kable_styling(full_width = FALSE, position = "center")
  
  # Plot AUC distributions
  plot <- ggplot(auc_results, aes(x = AUC, fill = Test_Group)) +
    geom_density(alpha = 0.7) +  # Density plot with transparency
    labs(title = "Density Plot of AUC Distributions for Train-Test Scenarios",
         x = "AUC",
         y = "Density",
         caption = "Data represents bootstrap samples") +
    theme_minimal() +  # Use a minimal theme for a clean look
    scale_fill_viridis_d(option = "magma", begin = 0.2, end = 0.8) +  # Use the "magma" palette from viridis
    theme(plot.title = element_text(hjust = 0.5, size = 14),  # Center and style title
          axis.title.x = element_text(size = 12),
          axis.title.y = element_text(size = 12),
          axis.text.x = element_text(size = 12),
          axis.text.y = element_text(size = 12),
          legend.title = element_blank())  # Remove legend title for simplicity
  
  # Return results
  return(list(
    mean_auc = mean_auc_apa,       # APA-formatted mean AUC table
    AUC_result = auc_results_apa,  # APA-formatted bootstrap AUC table
    anova_result = anova_summary,  # Summary of the ANOVA test
    visualisation = plot))         # Density plot visualizing the AUC distribution
}
```
